A supertree pipeline for summarizing phylogenetic and taxonomic information for millions of species

### 2017-01-23 doc/paper1-submission/paper5.tex
Mention that weights are not weights of evidence.

These optimality criteria help to define what it means for the supertree
to represent the input trees, as well as justifying and explaining
why various features of the supertree exist. The pipeline described
below produces a supertree that satisfies the first three optimality
criteria and is a greedy approximation of a solution to the fourth
goal. It is not guaranteed to display as many input nodes as possible.
Even if the summary tree does accomplish goal 4, it is not necessarily
a \emph{unique} optimum. The pipeline takes a greedy approach to producing
a summary tree by attempting to add groupings from the trees in order
of the trees ranking. This can be viewed as a greedy solution to the
problem of finding the tree with the maximum sum of displayed groups'
weighted scores criterion (MSDGWS, described in the appendix A) where the
weights from the trees are so extreme that displaying one group from
a highly ranked tree is preferred to displaying all of the groupings
from lower ranked trees.
Note that in this extreme form of weighting, we do not have to calculate
the score of a tree, we simply traverse the groupings by order of rank
and add a group if it is compatible with the previously added groups.

>>>>

These optimality criteria help to define what it means for the supertree
to represent the input trees, as well as justifying and explaining
why various features of the supertree exist. The pipeline described
below produces a supertree that satisfies the first three optimality
criteria and is a greedy approximation of a solution to the fourth
goal. It is not guaranteed to display as many input nodes as possible.
Even if the summary tree does accomplish goal 4, it is not necessarily
a \emph{unique} optimum. The pipeline takes a greedy approach to producing
a summary tree by attempting to add groupings from the trees in order
of the trees ranking. This can be viewed as a greedy solution to the
problem of finding the tree with the maximum sum of displayed groups'
weighted scores criterion (MSDGWS, described in the appendix A) where the
weights from the trees are so extreme that displaying one group from
a highly ranked tree is preferred to displaying all of the groupings
from lower ranked trees.  These large weights help to achieve our goal of allowing curators to fix problems in the tree.  While it is possible to view our pipeline as an optimization algorithm by assigning weights to the input trees in this way, we are not trying to weight the evidence in the input trees, and we do not actually ever calculate these weights in our pipeline.
Note that in this extreme form of weighting, we do not have to calculate
the score of a tree, we simply traverse the groupings by order of rank
and add a group if it is compatible with the previously added groups.
